Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-03-25 paper/zhang-cook-laa-langrene-menendez.Rmd
introduction modified
conclusions

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE,
                      root.dir = here::here(), 
                      fig.path = here::here("figs/"), 
                      cache = TRUE,
                      fig.align = "center",
                      fig.height = 3,
                      out.width = "100%")
```

@@

The remainder of the paper is organised as follows. 
The next section provides an overview of optimisation methods, specifically line search methods.  A review of the projection pursuit guided tour, an overview of the optimisation problem and outlines of three existing algorithms follows.
The third section presents the new visual diagnostics, including the the design of a data structure to capture information during the optimisation, from which several diagnostic plots are created.
An illustration of how the diagnostic plots can be used to examine the performance of different optimisers and guide improvements to the existing algorithms applications is shown using simulated data.
Finally, an explanation of the \ref{implementation} in the R package, \CRANpkg{ferrn} [@ferrn], is provided.

@@

This paper has set up a data object that can be used for diagnosing a complex optimisation procedure. The ideas were illustrated using the optimisers available for projection pursuit guided tour. Here the constraint is the orthonormality condition of the projection bases. The approach used broadly applies to other constrained optimisers.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE,
                      root.dir = here::here(), 
                      fig.path = here::here("figs/"), 
                      cache = TRUE,
                      fig.align = "center",
                      fig.height = 3,
                      fig.retina = 5,
                      out.width = "100%")
```

@@

The remainder of the paper is organised as follows. 
The next section provides an overview of optimisation methods, specifically line search methods.  A review of the projection pursuit guided tour, an overview of the optimisation problem and outlines of three existing algorithms follows.
The third section presents the new visual diagnostics, including the the design of a data structure to capture information during the optimisation, from which several diagnostic plots are created.
An illustration of how the diagnostic plots can be used to examine the performance of different optimisers and guide improvements to the existing algorithms applications is shown using simulated data.
Finally, an explanation of the implementation in the R package, \CRANpkg{ferrn} [@ferrn], is provided.

@@

This paper has provided several visual diagnostics that can be used for diagnosing a complex optimisation procedure. The methods were illustrated using the optimisers available for projection pursuit guided tour. Here the constraint is the orthonormality condition of the projection bases. The approach used broadly applies to other constrained optimisers.
